Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-08-07 paper/paper.tex
Fuller figured

% \begin{figure*}[tb]
%     \includegraphics*{gen-graph-as-plain.pdf}
%     \hfill
%     \includegraphics*{gen-graph-as-33v.pdf}
%     \hfill
%     \includegraphics*{gen-graph-as-33ved.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-as-plain-connected.pdf}
%     \hfill
%     \includegraphics*{gen-graph-as-33ve-connected.pdf}
%     \hfill
%     \includegraphics*{gen-graph-as-sip.pdf}
% 
%     \caption{Aggregate speedups.}
% \end{figure*}

@@

\begin{figure}[tb]
    \hfill
    \includegraphics{gen-graph-as-clique.pdf}
    \hfill

@@

>>>>

\subsection{A Closer Look at Clique}

@@

\begin{figure}[tb]
    \includegraphics{gen-graph-as-clique.pdf}

@@

\subsection{A Closer Look at $k{\downarrow}$}

\begin{figure}[tb]
    \includegraphics*{gen-graph-scatter-plain-kdown-vs-kdown-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-sip-kdown-vs-kdown-par-t32.pdf}

    \includegraphics{gen-graph-as-kdown.pdf}

    \caption{On the top row, per-instance speedups, using the $k{\downarrow}$ algorithm. The
    $x$-axis is sequential performance and the $y$-axis is 32 threaded performance. Below,
    aggregate speedups for both families.}
\end{figure}

\subsection{A Closer Look at McSplit}

\begin{figure}[tb]
    \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33v-mcsplit-vs-mcsplit-par-t32.pdf}

    \includegraphics*{gen-graph-scatter-33ved-mcsplit-vs-mcsplit-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-connected-mcsplit-vs-mcsplit-par-t32.pdf}

    \includegraphics*{gen-graph-scatter-33ve-connected-mcsplit-vs-mcsplit-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-sip-mcsplit-vs-mcsplit-par-t32.pdf}

    \includegraphics{gen-graph-as-mcsplit.pdf}

    \caption{On the top three rows, per-instance speedups, using the splitting algorithm. The
    $x$-axis is sequential performance and the $y$-axis is 32 threaded performance. On the final
    row, aggregate speedups for both families.}
\end{figure}

\subsection{Old Text}
